\pkg{cubble}: An R Package for Structuring Spatio-temporal Data

### 2022-02-23 main.Rmd
refine abstract again

---
documentclass: jss
author:
  - name: H. Sherry Zhang
    affiliation: Monash University
    address: 21 Chancellors Walk, Clayton VIC 3800 Australia
    email: \email{huize.zhang@monash.edu}
  - name: Dianne Cook
    affiliation: 'Monash University \AND'
    address: 21 Chancellors Walk, Clayton VIC 3800 Australia
    # location: Melbourne, Australia
    email:  dicook@monash.edu
  - name: Ursula Laa
    affiliation: 'University of Natural Resources and Life Sciences \AND'
    address: Gregor-Mendel-Straße 33, 1180 Wien, Austria
    email:  ursula.laa@boku.ac.at
  - name: Nicolas Langrené
    affiliation: 'BNU-HKBU United International College \AND'
    address: 2000 Jintong Road, Tangjiawan, Zhuhai, Guangdong Province, China
    email: nicolas@langrene.com
  - name: Patricia Menéndez
    affiliation: 'Monash University \AND'
    address: 21 Chancellors Walk, Clayton VIC 3800 Australia
    email:  patricia.menendez@monash.edu
title:
  formatted: "\\pkg{cubble}: An R Package for Structuring Spatio-temporal Data"
  # If you use tex in the formatted title, alsoge supply version without
  plain:     "cubble: An R Package for Structuring Spatio-temporal Data"
  # For running headers, if needed
  # short:     "\\pkg{foo}: A Capitalized Title"
abstract: >

  \textcolor{red}{start with describing the data: spatial and temporal, then what's the problem, then propose cubble.}

  \textcolor{red}{Exploring spatio-temporal data can sometimes be discouraging given the various different formats spatio-temporal data can present themselves in practice}. Moreover, the two observational units naturally exist in spatio-temporal data \textcolor{red}{can cost analysts many time and efforts} on organising variables and results and switching between a single table and multiple tables in the analysis. In this paper, a new data structure, \code{cubble}, is proposed for wrangling and visualising spatio-temporal data. The new data structure uses a single data object to organise spatial and temporal variables in two forms so that they can be wrangled separately while keep syncronised. Advanced considerations are given to illustrate data with hierarchical structure, data matching, how cubble fits with the interactive graphics pipeline, and spatio-temporal transformation. Examples are given to analysing Australia meteorology data, river level data, and climate reanalysis (ERA5). 
keywords:
  # at least one keyword must be supplied
  formatted: [spatial, temporal, spatio temporal, "\\proglang{R}", environmental data, exploratory data analysis]
  plain:     [spatial, temporal, spatio temporal, R, environmental data, exploratory data analysis]
preamble: >
  \usepackage{amsmath}
  \usepackage{array}
  \usepackage{xcolor}
output: rticles::jss_article
bibliography: references.bib
---

>>>>

---
documentclass: jss
author:
  - name: H. Sherry Zhang
    affiliation: Monash University
    address: 21 Chancellors Walk, Clayton VIC 3800 Australia
    email: \email{huize.zhang@monash.edu}
  - name: Dianne Cook
    affiliation: 'Monash University \AND'
    address: 21 Chancellors Walk, Clayton VIC 3800 Australia
    # location: Melbourne, Australia
    email:  dicook@monash.edu
  - name: Ursula Laa
    affiliation: 'University of Natural Resources and Life Sciences \AND'
    address: Gregor-Mendel-Straße 33, 1180 Wien, Austria
    email:  ursula.laa@boku.ac.at
  - name: Nicolas Langrené
    affiliation: 'BNU-HKBU United International College \AND'
    address: 2000 Jintong Road, Tangjiawan, Zhuhai, Guangdong Province, China
    email: nicolas@langrene.com
  - name: Patricia Menéndez
    affiliation: 'Monash University \AND'
    address: 21 Chancellors Walk, Clayton VIC 3800 Australia
    email:  patricia.menendez@monash.edu
title:
  formatted: "\\pkg{cubble}: An R Package for Structuring Spatio-temporal Data"
  # If you use tex in the formatted title, alsoge supply version without
  plain:     "cubble: An R Package for Structuring Spatio-temporal Data"
  # For running headers, if needed
  # short:     "\\pkg{foo}: A Capitalized Title"
abstract: >
  Spatio-temporal data have two types of variables: spatial variables have fixed value across time in the same location while temporal variables need both the location and timestamp to identify its value. These variables can be organised in two separate tables, each focusing on one aspect of the data, or a single table that combines all the variables together. For exploratory data analysis and visualisation, analysts needs both formats for different types of exploration, while it can be tedious to constantly split and join variables in order to cast the data into the desireable shape. In this paper, a new data structure, \code{cubble}, is proposed for exploring spatio-temporal data. The new data structure organises spatial and temporal variables as two forms of a single data object so that they can be wrangled separately while keep syncronised. Considerations are given to data with hierarchical structure, data matching and explain how \pkg{cubble} fits in with the interactive graphics pipeline and spatio-temporal transformation. Examples are given to analysing Australia meteorology data, river level data, and climate reanalysis (ERA5) data. 
keywords:
  # at least one keyword must be supplied
  formatted: [spatial, temporal, spatio temporal, "\\proglang{R}", environmental data, exploratory data analysis]
  plain:     [spatial, temporal, spatio temporal, R, environmental data, exploratory data analysis]
preamble: >
  \usepackage{amsmath}
  \usepackage{array}
  \usepackage{xcolor}
output: rticles::jss_article
bibliography: references.bib
---

### 2022-02-23 main.tex
refine abstract again

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

@@

\Abstract{
\textcolor{red}{start with describing the data: spatial and temporal, then what's the problem, then propose cubble.}
\textcolor{red}{Exploring spatio-temporal data can sometimes be discouraging given the various different formats spatio-temporal data can present themselves in practice}.
Moreover, the two observational units naturally exist in spatio-temporal
data \textcolor{red}{can cost analysts many time and efforts} on
organising variables and results and switching between a single table
and multiple tables in the analysis. In this paper, a new data
structure, \code{cubble}, is proposed for wrangling and visualising
spatio-temporal data. The new data structure uses a single data object
to organise spatial and temporal variables in two forms so that they can
be wrangled separately while keep syncronised. Advanced considerations
are given to illustrate data with hierarchical structure, data matching,
how cubble fits with the interactive graphics pipeline, and
spatio-temporal transformation. Examples are given to analysing
Australia meteorology data, river level data, and climate reanalysis
(ERA5).
}

@@

% Pandoc citation processing

% Pandoc header

>>>>

@@

\Abstract{
Spatio-temporal data have two types of variables: spatial variables have
fixed value across time in the same location while temporal variables
need both the location and timestamp to identify its value. These
variables can be organised in two separate tables, each focusing on one
aspect of the data, or a single table that combines all the variables
together. For exploratory data analysis and visualisation, analysts
needs both formats for different types of exploration, while it can be
tedious to constantly split and join variables in order to cast the data
into the desireable shape. In this paper, a new data structure,
\code{cubble}, is proposed for exploring spatio-temporal data. The new
data structure organises spatial and temporal variables as two forms of
a single data object so that they can be wrangled separately while keep
syncronised. Considerations are given to data with hierarchical
structure, data matching and explain how \pkg{cubble} fits in with the
interactive graphics pipeline and spatio-temporal transformation.
Examples are given to analysing Australia meteorology data, river level
data, and climate reanalysis (ERA5) data.
}

@@

% tightlist command for lists without linebreak
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
